Issues with Dynamical Measurements Across the Disk

### 2019-02-15 paper/ms.tex
Various small fixes

\section{Discussion} \label{sec:discussion}
We have shown that, in simulation, the ``local midplane'' can have strong
azimuthal dependence. The implications of this finding are not clear, but
clearly demonstrate that assuming our local midplane is the same as the global
midplane is insufficient for extracting the most dynamical information from
the {\em Gaia} mission. From now on, we set aside the discussion of
inaccuracies in the Solar radius. While all that we state about the midplane
applies to the Solar radius as well, it is not clear the best way to determine
the dynamical center of the galaxy in the FIRE simulations.

@@

A possible interpretation of our finding is that one should use a star's local
midplane in order to compute dynamical quantities like the vertical action.
Under the assumption that this interpretation is correct, we now consider the
implications for dynamical studies of disrupting open clusters (the original
motivation of this study).

Suppose an open cluster of mass $m_c$ on an orbit with actions $\bm{J}_c$ is
disrupted, and that the cluster is currently at an orbit phase of
$\bm{\theta}_0$. We would like to determine all stars in the {\em Gaia}
dataset\footnote{This is likely to be more successful with DR3/4 than DR2,
since upcoming data releases will contain a far greater number of stars with
radial velocities --- though targeted, follow-up radial velocity surveys may
allow this program to be performed sooner.} that are likely to be ejected
members from that cluster. One could proceed by integrating the cluster's
orbit and selecting all stars within a certain distance of that orbit,
accounting for the fact that the stream will not exactly follow the orbit of
the cluster \citep[e.g.][]{2011MNRAS.413.1852E}.

@@

For the thick orbit (brown), the neighborhood is at the maximum value for
nearly all masses, except at the very low-mass end in m12i.

>>>>

\section{Discussion} \label{sec:discussion}
We have shown that, in simulation, the ``local midplane'' can have strong
azimuthal dependence. The implications of this finding are not clear, but
clearly demonstrate that assuming our local midplane is the same as the global
midplane is insufficient for extracting the most dynamical information from
the {\em Gaia} mission. We focus our discussion now solely on the midplane.

@@

A possible interpretation of our finding is that one should use a star's local
midplane in order to compute dynamical quantities like the vertical action.
Under the assumption that this interpretation is correct, we now consider the
implications for attempts to reconstruct disrupting open clusters by selecting
ejected members based on their actions.

Suppose an open cluster of mass $m_c$ on an orbit with actions $\bm{J}_c$ is
disrupted. We would like to determine all stars in the {\em Gaia}
dataset\footnote{This is likely to be more successful with DR3/4 than DR2,
since upcoming data releases will contain a far greater number of stars with
radial velocities --- though targeted, follow-up radial velocity surveys may
allow this program to be performed sooner.} that are likely to be ejected
members from that cluster. One could generate an initial catalogue of
candidate members by integrating the cluster's orbit and selecting stars close
to that orbit, accounting for the fact that the stream will not exactly follow
the orbit of the cluster \citep[e.g.][]{2011MNRAS.413.1852E}.

@@

For the thick-disk orbit (brown), the neighborhood is at the maximum value for
nearly all masses, except at the very low-mass end in m12i.
